%\nonstopmode
\documentclass[twocolumn, a4paper, fontsize=9pt, headsepline, footsepline]{scrartcl}
\usepackage[
  top=25mm,
  bottom=19mm,
  left=13mm,
  right=13mm,
  headheight=15mm,
]{geometry}
\setlength{\footheight}{12mm}
\usepackage[hidelinks]{hyperref}

% Change the theme here (light, dark, BW, blue, green)
\usepackage{tagging}
\usetag{##THEME##}

\usepackage{fontspec}
\setmainfont[Ligatures=TeX]{Montserrat}
\setmonofont[Scale=0.9]{IBM Plex Mono}

\setlength{\parindent}{5mm}

\usepackage{setspace}
\RedeclareSectionCommands[
  beforeskip=2mm plus 1mm minus 1mm,
  afterskip=1.5mm plus 1mm minus 1mm
]{section,subsection}

\setkomafont{pagehead}{\normalfont}
\setkomafont{section}{\Large\bfseries}
\setkomafont{subsection}{\normalsize}

\usepackage{scrlayer-scrpage}
\usepackage{fontawesome}
\renewcommand*{\faicon}[1]{\makebox[1.5em][c]{\csname faicon@#1\endcsname}}
\ihead{\Huge Brooks J Rady \\\large Student at The University of Sheffield}
\ohead{Sheffield, UK\hspace{2mm}\faMapMarker \\ +44 7413 390609\hspace{2mm}\faPhoneSquare \\ b.j.rady@gmail.com\hspace{2mm}\faEnvelopeSquare}
\cfoot{}
\ifoot{\textbf{REFERENCES}\\\footnotesize Mr. Vernon Caswell, AP Computer Science Teacher
  at PRA <vcaswell@prospectridgeacademy.org>\\ Dr. Stephane Mesnage,
  Microbiologist at The University of Sheffield <s.mesnage@sheffield.ac.uk>}
\ofoot{linkedin.com/in/bjrady/\hspace{2mm}\faLinkedinSquare\\thelostlambda.xyz\hspace{2mm}\faGlobe}

\ModifyLayer[addvoffset=-1mm]{scrheadings.foot.above.line}
\ModifyLayer[addvoffset=-1mm]{plain.scrheadings.foot.above.line}
\ModifyLayer[addvoffset=1mm]{scrheadings.head.below.line}
\ModifyLayer[addvoffset=1mm]{plain.scrheadings.head.below.line}

\usepackage{xcolor}
\definecolor{bg}{RGB}{40,40,40}
\definecolor{fg}{RGB}{200,200,200}
\definecolor{rot}{RGB}{244,96,54}
\definecolor{lila}{RGB}{181,68,110}
\definecolor{hellblau}{RGB}{10,205,187}
\definecolor{grun}{RGB}{112,174,110}
\tagged{BW}{\definecolor{rot}{RGB}{0,0,0}}
\tagged{BW}{\definecolor{lila}{RGB}{0,0,0}}
\tagged{BW}{\definecolor{hellblau}{RGB}{0,0,0}}
\tagged{BW}{\definecolor{grun}{RGB}{0,0,0}}
\tagged{green}{\definecolor{rot}{RGB}{122, 199, 76}}
\tagged{green}{\definecolor{lila}{RGB}{122, 199, 76}}
\tagged{green}{\definecolor{hellblau}{RGB}{122, 199, 76}}
\tagged{green}{\definecolor{grun}{RGB}{122, 199, 76}}
\tagged{blue}{\definecolor{rot}{RGB}{99, 121, 134}}
\tagged{blue}{\definecolor{lila}{RGB}{99, 121, 134}}
\tagged{blue}{\definecolor{hellblau}{RGB}{99, 121, 134}}
\tagged{blue}{\definecolor{grun}{RGB}{99, 121, 134}}
\tagged{dark}{\pagecolor{bg}}
\tagged{dark}{\color{fg}}

\usepackage{soul}

\usepackage{enumitem}
\setlist{nosep}

\begin{document}
\setulcolor{rot}
\setul{}{2pt}
\section*{\ul{OBJECTIVE}}
\noindent
A perpetually curious student with a keen interest in molecular biology and
computer science. Seeking to engage in research and work alongside professionals
in the field to further mankind's understanding of the world.

\setulcolor{lila}
\section*{\ul{FORMAL EDUCATION}}
\subsection*{Molecular Biology at The University of Sheffield (2019-2023)}
\onehalfspacing
\emph{Prospective Mark: 1\textsuperscript{st} Class Honours}

\subsection*{Bioengineering at The University of Sheffield (2018-2019)}
\onehalfspacing
\emph{Weighted Average: 89.25\%}\par
\emph{Received the Sir Harold West Award}

\subsection*{Prospect Ridge Academy High School (2014-2018)}
\onehalfspacing
\emph{GPA: 4.741 (4.00)}\par
\emph{Graduated Summa Cum Laude}\par
\emph{Received National AP Scholar Award}\par
\emph{Received First Place for Senior Capstone Project}

\setulcolor{grun}
\section*{\ul{EXPERIENCE}}

\subsection*{Software Lead \& Co-Presenter (2019)\\\textmd{\emph{Member of the
    University iGEM Team, Sheffield UK}}}
\noindent
iGEM is a synthetic biology competition involving universities from around the
globe. Our team designed a low-cost, open-source microplate reader for use in
community labs. I developed the software that powered our device and presented
our project at the Jamboree in Boston, Massachusetts.
\begin{itemize}
\item Designed custom sensor and control electronics
\item Developed firmware for an ESP32 using C
\item Built a web-interface using HTML, CSS, and JS
\item Exercised team communication and planning skills
\item Awarded Best Presentation in the UK
\item Won Best Open Project and Gold Medal in Boston
\end{itemize}

\subsection*{Programming Mentor \& Workshop Instructor
  (2018-Current)\\\textmd{\emph{Volunteer Teaching at the University, Sheffield UK}}}
\noindent
For the past couple of years I've been either helping to teach Python via
organisations like Cookies and Code, or have been running programming workshops
for the Sheffield Bionics Society. I've been both an entry-level and advanced
instructor, working with both individuals and large groups.
\begin{itemize}
\item Communicated complex concepts understandably
\item Demonstrated organisational and interpersonal skills
\item Developed existing skills in computer programming
\item Helped others leverage computation in their research
\end{itemize}

\subsection*{Lost in Translation: Proteins Post-Expression (2019)\\\textmd{\emph{Scientific Poster} — \url{http://bit.ly/36bKMPG}}}
\noindent
Scanning the literature, I stockpiled information regarding the
post-translational modification and trafficking of proteins. From this body of
research, I picked out the most important points to be presented as part of the
poster — striking the balance between rigour and brevity.
\begin{itemize}
\item Selected key points from a large body of research
\item Demonstrated a competency in graphical design
\item Elucidated the connections between concepts 
\end{itemize}

\subsection*{Creepy Phenomena: An Investigation of Viscoelasticity
  (2019)\\\textmd{\emph{Scientific Report} — \url{http://bit.ly/2PkNP2b}}}
\noindent
As part of a university physics course, I wrote a report analysing an
experimental video showcasing a particular viscoelastic model. Working backwards
from only the video and the volume of the syringe, the fundamental constants of
the system were calculated.\par
\begin{itemize}
\item Used maths and statistics to model a physical system
\item Demonstrated writing and problem solving skills
\item Created a report using LaTeX, R, and Knitr
\end{itemize}

\subsection*{Founder of PRA Robotics (2014-2018)\\\textmd{\emph{Prospect Ridge
    Academy, Colorado USA}}}
\noindent
The PRA robotics team competed in both the First Tech Challenge (FTC) and the
Autonomous Vehicle Competition (AVC). The team has now grown to several dozen
members and continues foster students' interest in robotics.
\begin{itemize}
\item Led software development for both FTC and AVC
\item Ran Java programming workshops for new recruits
\item Competed as finalists in the FTC State Championship
\item Developed skills in autonomous control engineering
\item Showed leadership skills by managing a large team
\end{itemize}

\subsection*{\textbf{\texttt{FTC\_HTTP}}: Wireless FTC Robot Programming Tool
  (2017)\\\textmd{\emph{Cross-platform CLI Application} — \url{http://bit.ly/ftc_http}}}
\noindent
FTC teams used to be forced to choose between two programming toolchains: either
a 5GB+ install and minute-long programming cycles, or an under-featured
web-interface prone to code loss. By reverse engineering the web protocol,
\texttt{FTC\_HTTP} allows wireless development from any text-editor, on any platform, in
less than 8MB.
\begin{itemize}
\item Reverse engineered an undocumented protocol
\item Created a polished, cross-platform application
\item Demonstrated skills in Rust, HTTP, and Git
\item Produced documentation and a video tutorial
\item Shared the application with others during FTC events
\end{itemize}

\subsection*{Assistant Researcher (2016-2017)\\\textmd{\emph{Summer Placement at Avidity LLC, Colorado USA}}}
\noindent
During my time at Avidity, I designed a set of DNA tethers for use in
multiplexed pathogen assays, worked on a directed evolution project, and
explored the manufacture of lateral flow assays on an aluminium surface.
\begin{itemize}
\item Developed extensive wet-lab and digital biology skills
\item Applied recombinant DNA technologies
\item Showcased an aptitude for independent research
\end{itemize}

% DIRTY CHUNK !!!

Add stuff about Bionics here (taught programming, electronics, and design)

Ethical Hacking, more teaching experience in Cyber security / Linux fields

Exercism is a nice bit of open source teaching and programming work

Zellij is my primary open-source project now – lots of good, international
teamwork

Avalon was some electrical engineering experience and practice making PCBs

Evolutor is my engineering magnum opus so far, 3D design, electronics, and software

Add my nationality somewhere (so people know I'm international status)

Add languages as well (mostly just English, obviously, but with a bit of German)

Other open-source stuff could be worth mentioning...

Starting up iGEM again is something that's noteworthy!

PGFinder work + Graph Generator + MS/MS pipeline with Mesnage

Project Hex, more engineering / robotics / programming

PAL teaching of biology to first-year students

MBB society as academic officer (working with staff)

Growbotics work is an in to the plant side of things!

Add both new essays (Rhizobia & Hydrolases)

Academic Awards:
  - Paul Hancock Prize (Best overall mark in L2 practical module)
  - Valerie Broomhead Prize (Best overall mark in L1 practical module)

% END DIRTY CHUNK

\onecolumn
\setulcolor{hellblau}
\section*{\ul{ADDITIONAL WORK}}
\subsection*{Personal Web Server (2015-Current)\\\textmd{\emph{File-Sync, VPN,
    DLNA, FTP, Games, and Website} — \url{http://thelostlambda.xyz/}}}
\subsection*{Sickle Cell Disease: Symptoms, Molecular Basis, and Treatments
(2019)\\\textmd{\emph{A Review Focused on Sickle Cell Pathogenesis} — \url{http://bit.ly/2E7Yu9x}}}
\subsection*{Tissue Who? — A Foray into Histology and Tissue Identification
  (2019)\\\textmd{\emph{A Short Histology Primer \& Lab Report} —
    \url{http://bit.ly/2ooernJ}}}
\subsection*{Under Pressure — Hydrostatics and Elastic Tube Distention
  (2019)\\\textmd{\emph{Modelling a Biophysical System from Data} — \url{http://bit.ly/2qMQmYA}}}
\subsection*{In Vivo Detection and Signaling of Arbitrary DNA Sequences
  (2018)\\\textmd{\emph{Highschool Capstone Project Exploring a Novel Use for
    CRISPR} — \url{http://bit.ly/2pbA9fk}}}
\subsection*{Pokéstats — What Type Of Pokemon Is The Match For You?
  (2018)\\\textmd{\emph{A Statistical Report Exploring a Large Pokémon Dataset} — \url{http://bit.ly/2FVjMqh}}}
\subsection*{The Regicide of the Fisher King (2018)\\\textmd{\emph{AP English
    Literature Modernism Essay} — \url{http://bit.ly/2FHoYSy}}}
\subsection*{Honors Physics “Build a Planet” Project (2017)\\\textmd{\emph{Exploring and
    Mathematically Modelling the Physics of a Fictional Planet} — \url{http://bit.ly/2IA9f5F}}}
\setulcolor{rot}
\section*{\ul{SELECTED AWARDS \& CERTIFICATES}}
\begin{itemize}
\item Won Best Open Project \& Gold Medal during iGEM Jamboree (2019)
\item Awarded Best Presentation during iGEM UK Meetup (2019)
\item Best Communicated Solution during EWB Global Engineering Challenge (2019)
\item Linnaeus Award for Excellence in Biology (2018)
\item Hacker Award for Excellence in Computer Science (2018)
\item National Honor Society (2017-2018)
\item Prospect Ridge Academy High Honor Roll (2015-2018)
\item Design Award \& Finalist Alliance at FTC State Championship (2017-2018)
\item Second place in Junior Energy and Transportation at Colorado Science and
  Engineering Fair (2014)
\item First place in Alternative Fuels at Denver Metro Science Fair (2014)
\end{itemize}
\setulcolor{grun}
\section*{\ul{HOBBIES \& INTERESTS}}
\noindent
I'm into just about anything that bytes. When I'm not fiddling with programming
or one of my computers, I indulge myself in video games. I've built the computer
I play games on and have helped a number of others do the same. Since coming to
Uni, I've developed an interest in cybersecurity and have joined the Sheffield
Ethical Student Hackers.

Aside from computers, I've recently taken up photography. I can't draw to save
my life, but I think I've gotten rather good at stealing art from
nature. Photography for me is a fun blend of technical knowledge and artistic
challenge.

Finally, I love to read and to write. I often end up doing lots of technical
reading as a consequence of my computer science hobby, but certainly enjoy an
awful fantasy novel when I can find the time for it.
\end{document}
 
